On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-10 paper/paper.tex
wibble

In this paper, a representation of pattern matching was given in the form of a
GADT called \verb|E|. A GHC plugin is then used to transform code written in a
subset of Haskell containing algebraic data types, pattern matching, tail
recursion and lambdas into values of this GADT. A backend can then use these
\verb|E a| values to interpret the Haskell code, compile it or otherwise
manipulate it.

>>>>

In this paper, a representation of pattern matching was given in the form of a
GADT called \verb|E|. A GHC plugin is then used to transform code written in a
subset of Haskell consisting of algebraic data types, pattern matching, tail
recursion and lambdas into values of this GADT. A backend can then use these
\verb|E a| values to interpret the Haskell code, compile it or otherwise
manipulate it.
